Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-05-28 manuscript/manuscript.Rmd
updates ms with new climate sensitivity figure

```{r figure_1, dependson="plot-options", fig.cap="Sensitivity of equilibrium cover to removal of climate effects from each vital rate regression.", fig.width=4.5, fig.height=6, cache=FALSE, results='hide'}
setwd("../montana/ipm/simulations/sensitivity_results/")
files <- list.files()
cover_files <- files[grep("cover", files)]
spp_id <- substr(cover_files, 1, 4)
clim_id <- rep(c("allClim", "noPpt", "noTemp",
                 "noPpt", "noTemp",
                 "noPpt", "noTemp"), 4)
vital_id <- rep(c("All", "Growth", "Growth",
                  "Survival", "Survival",
                  "Recruitment", "Recruitment"), 4)
num_files <- length(cover_files)
all_sims <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(i in 1:num_files){
  tmp <- read.csv(cover_files[i])
  tmp$species <- rep(spp_id[i], nrow(tmp))
  tmp$sim <- rep(clim_id[i], nrow(tmp))
  tmp$vital <- rep(vital_id[i], nrow(tmp))
  all_sims <- rbind(all_sims, tmp)
}
all_sims <- all_sims[2:nrow(all_sims),]
all_clim_sims <- subset(all_sims, vital=="All")

@@

mean_cover <- ddply(subset(equilibrium_cover, sim=="allClim"), .(species), summarise,
                    value = mean(eq_cover))

>>>>

```{r figure_1, dependson="plot-options", fig.cap="Sensitivity of equilibrium cover to removal of climate effects from each vital rate regression.", fig.width=4.5, fig.height=6, cache=FALSE, results='hide'}
setwd("../montana/ipm/simulations/sensitivity_results/")
files <- list.files()
cover_files <- files[grep("cover", files)]
spp_id <- substr(cover_files, 1, 4)
clim_id <- rep(c("noClim", "Ppt", "Temp",
                 "Ppt", "Temp",
                 "Ppt", "Temp"), 4)
vital_id <- rep(c("All", "Growth", "Growth",
                  "Survival", "Survival",
                  "Recruitment", "Recruitment"), 4)
num_files <- length(cover_files)
all_sims <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(i in 1:num_files){
  tmp <- read.csv(cover_files[i])
  tmp$species <- rep(spp_id[i], nrow(tmp))
  tmp$sim <- rep(clim_id[i], nrow(tmp))
  tmp$vital <- rep(vital_id[i], nrow(tmp))
  all_sims <- rbind(all_sims, tmp)
}
all_sims <- all_sims[2:nrow(all_sims),]
all_clim_sims <- subset(all_sims, vital=="All")

@@

mean_cover <- ddply(subset(equilibrium_cover, sim=="noClim"), .(species), summarise,
                    value = mean(eq_cover))
